### 2020-05-09 ncov.tex
bmb suggestions!

@@

\section*{Abstract}
A novel coronavirus (SARS-CoV-2) has recently emerged as a global threat in December 2019. 
As the epidemic progresses, disease modelers continue to focus on estimating the basic reproductive number \Ro\ --- the average number of secondary cases caused by a primary case in an otherwise susceptible population.
The modeling approaches and resulting estimates of \Ro during the beginning of the outbreak vary widely, despite relying on similar data sources.
Here, we present a novel statistical framework for comparing and combining different estimates of \Ro across a wide range of models by decomposing the basic reproductive number into three key quantities: the exponential growth rate, the mean generation interval, and the generation-interval dispersion.
We then apply our framework to early estimates of \Ro for the SARS-CoV-2 outbreak.
We show that many early \Ro estimates are overly confident.
Our results emphasize the importance of propagating uncertainties in all components of \Ro, including the shape of the generation-interval distribution, in efforts to estimate \Ro at the outset of an epidemic.

@@

As SARS-CoV-2 began to spread in other parts of China, outside Hubei province, as well as in other countries, many analyses of the outbreak were published as pre-prints (e.g., \cite{bedfordncov, imaincov, liuncov, majumderncov, readncov, zhaoncov}) and in peer-reviewed journals (e.g., \cite{li2020early, riou2020pattern, wu2020nowcasting, zhao2020preliminary}).
These analyses particularly focused on estimating the basic reproductive number \Ro\ --- the average number of secondary cases generated by a primary case in a fully susceptible population \citep{anderson1991infectious, diekmann1990definition} --- in order to assess the pandemic potential of SARS-CoV-2.
Such rapid dissemination of the early analyses played an important role in shaping the response to the outbreak \citep{majumder2020early}.

We commend these researchers for their timely contribution and those who made the data publicly available.
However, the estimates of \Ro from different research groups (as well as the associated degrees of uncertainty) vary significantly even though most analyses relied on reports of confirmed cases from China, particularly from the Hubei province.
Comparing a disparate set of estimates of \Ro can be particularly difficult when the estimation methods and their underlying assumptions vary widely.
In some cases, similar methods can give different estimates; in other cases, different methods can give similar estimates.
Understanding the differences (or similarities) between \Ro estimates is critical to controlling an epidemic as \Ro provides information about the level of intervention required to prevent further transmission \citep{anderson1991infectious}, and about the potential final size of the outbreak \citep{anderson1991infectious, ma2006generality}.

Here, we show that a wide range of approaches to estimating \Ro can be understood and compared in terms of estimates of three quantities: the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$.
The generation interval, defined as the interval between the time when an individual becomes infected and the time when that individual infects another individual \citep{svensson2007note}, characterizes the relationship between $r$ and \Ro \citep{wearing2005appropriate, roberts2007model, wallinga2007generation, park2019practical};
therefore, estimates of \Ro directly depend on their assumptions about the generation-interval distribution and the exponential growth rate.
Early in an epidemic, information is scarce and there is inevitably a great deal of uncertainty surrounding both case reports (affecting the estimates of the exponential growth rate) and contact tracing (affecting the estimates of the generation-interval distribution).
Ignoring these uncertainties inevitably leads to overly confident conclusions.
We suggest that disease modelers should make sure their assumptions about these three quantities are clear and reasonable, and that estimates of uncertainty in \Ro should propagate error from all three sources \citep{elderd2006uncertainty}.

We present a statistical framework for averaging across estimates of basic reproductive number \Ro from multiple studies and apply the method to seven disparate models published online as pre-prints between January 23--26, 2020 that estimated \Ro for the SARS-CoV-2 outbreak \citep{bedfordncov, imaincov, liuncov, majumderncov, readncov, riouncov, zhaoncov}.
Previous studies have directly calculated the average of reported \Ro values  \citep{majumder2020early, liu2020reproductive} but such methods can undermine differences in underlying model assumptions and statistical methods.
Instead, we decompose estimated \Ro into three key quantities ($r$, $\bar G$, and $\kappa$) and calculate the average (pooled estimates) of these key parameters.
Calculating \Ro based on the pooled estimates allow us to appropriately average across the uncertainties present in modeling approaches and their underlying assumptions.
We use these pooled estimates to illustrate the importance of propagating different sources of error, particularly uncertainty in both the growth rate and the generation interval.
% We also use our framework to tease apart which assumptions of these different models led to their different estimates and the associated degrees of uncertainty.

@@

\afterpage{%
\clearpage
    \begin{landscape}
\begin{table}[!th]
\begin{center}
\scriptsize
\begin{tabular}{l|p{2cm}|p{3.2cm}|p{2.8cm}|p{2.5cm}|p{2.4cm}|p{2.7cm}|p{2cm}}
 & Model & Data (study period) & Data source & Basic reproductive\newline number \Ro & Mean generation\newline interval $\bar G$ (days) & Generation-interval\newline dispersion $\kappa$ & Reference \\
\hline
Study 1 & Deterministic branching process model & Total number of cases in Wuhan City, China\newline (Jan 18, 2020) & Estimated by \cite{imaincov0} & 1.5--3.5 & 10 & 1 & \cite{bedfordncov} \\
\hline
Study 2 & Stochastic branching process model & Total number of cases in Wuhan City, China\newline (Jan 18, 2020) & Estimated by \cite{imaincov0}  & 2.6 (1.5--3.5)$^\ast$ & 8.4 & Not reported$^\dagger$ & \cite{imaincov} \\
\hline
Study 3 & Poisson offspring distribution model & Confirmed cases from China and other countries\newline (Dec 29, 2019--Jan 23, 2020) & Medical records and epidemiological investigations from Guangdong Province, China, and official websites of other regions in China & 2.92 (95\% CI: 2.28--3.67) & 8.4 & 0.2 & \cite{liuncov} \\
\hline
Study 4 & Metapopulation Susceptible-Exposed-Infected-Recovered (SEIR) model & Confirmed cases from China and other countries\newline (Jan 1--21, 2020) & Not reported & 3.8 (95\% CI: 3.6--4.0) & 7.6 & 0.5 & \cite{readncov} \\
\hline
Study 5 & Stochastic branching process model & Total number of cases in Wuhan City, China\newline (Jan 18, 2020) & Estimated by \cite{imaincov0} & 2.2 (90\% CI: 1.4--3.8) & 7--14 & 0.5 & \cite{riouncov} \\
\hline
Study 6 & Exponential growth model & Confirmed cases from China\newline (Jan 10--22, 2020) & Wuhan
Municipal Health Commission, China and National Health Commission of China & 5.47 (95\% CI: 4.16--7.10)$^\ddagger$ & 7.6--8.4 & 0.2 & \cite{zhaoncov} \\
\hline
Study 7 & Incidence Decay and Exponential Adjustment (IDEA) model & Reported cases from Wuhan City, China\newline (Dec 1, 2019--Jan 26, 2020) & World	Health Organization, National Health Commission of China, Wuhan Municipal	Health Commission, and \cite{huang2020clinical} & 2.0--3.1 & 6--10 & 0 & \cite{majumderncov} \\
\hline
\end{tabular}
\end{center}
\caption{
\textbf{Summary of the models, analyzed data, reported estimates of the basic reproductive number, and the assumptions about the generation-interval distributions.}
Model details, estimates of \Ro, and their assumptions about the shape of the generation interval distributions were collected from 7 studies.
Generation-interval dispersion represent the squared coefficient of variations in generation intervals.
$^\ast$These intervals reflect \Ro values for best and worst scenarios. We treat these intervals as a 90\% credible interval in our analysis.
$^\dagger$We assume $\kappa = 0.5$ in our analysis.
$^\ddagger$The authors presented \Ro estimates under different assumptions regarding the reporting rate; we use their baseline scenario in our analysis to remain consistent with other studies, which do not account for changes in the reporting rate.
}
\end{table}
\end{landscape}
\clearpage
}

We gathered information on estimates of \Ro and their model assumptions from 7 articles that were published online between January 23--26, 2020.
Five studies \citep{liuncov, majumderncov, readncov, riouncov, zhaoncov} were uploaded to pre-print servers (bioRxiv, medRxiv, and SSRN); one report was posted on the website of Imperial College London \citep{imaincov}; and one report was posted on \url{nextstrain.org} \citep{bedfordncov}.
Model details and corresponding data are summarized in Table 1.

@@

Despite a wide range of models considered across Study 1--7, all of them assume that the epidemic grows exponentially in the beginning.
The IDEA model (used in Study 7) includes a discount parameter $d$ that allows the model to deviate from the exponential growth when $d \neq 0$ \citep{fisman2013idea}, but Study 7 estimates $d=0$ across all parameters they consider.
Even though some studies consider reported cases up to Janaury 26, 2020 --- three days after the travel restriction that took place on January 23, 2020 \citep{Tianeabb6105} --- the exponential growth assumption can still describe the number of reported cases reasonably well;
given the incubation period of around 5 days \citep{lauer2020incubation} as well as reporting delay of around 5 days \citep{sun2020early}, the majority of reported cases during study periods are likely to have been infected prior to the travel ban.

When the epidemic is growing exponentially, the estimated basic reproductive number entirely depends on the exponential growth rate $r$ and the \emph{intrinsic} generation-interval distribution $g(\tau)$, which describes the infection time of secondary cases caused by a primary case in a fully susceptible population \citep{champredon2015intrinsic}, via the Euler-Lotka equation \citep{wallinga2007generation}:
\begin{linenomath*}
\begin{equation}
\frac{1}{\Ro} = \int \exp(-r\tau) g(\tau) \, d\tau.
\label{eq:euler}
\end{equation}
\end{linenomath*}
In other words, all model assumptions come down to assumptions about the exponential growth rate $r$ and the shape of the generation-interval distribution $g(\tau)$.
For example, if a model relies on strong assumptions about the underlying observation or process model, the estimated confidence or credible intervals associated with the exponential growth rates or parameters of the generation-interval distributions will be necessarily narrow.
Therefore, it is sufficient to consider the estimates and assumptions about the exponential growth rates and the shapes of the generation-interval distributions to understand disparate estimates of the basic reproductive number.

As most studies do not report their estimates of the exponential growth rate, we first summarize model outcomes using reported (either estimated or assumed) values of the basic reproductive number \Ro, mean generation interval $\bar G$ and generation-interval dispersion $\kappa$, represented by the squared coefficient of variation (Table 1);
we re-estimate the corresponding exponential growth rates from these values later.
Study 2 only reports their assumptions about the mean generation interval; for brevity, we assume $\kappa = 0.5$ in our analysis.
Study 6 presents \Ro estimates under 12 different scenarios regarding reporting rates (0, 0.5, 1 or 2 fold increase in reporting rate) and the shapes of the generation-interval distributions (MERS-like, SARS-like, and average);
we use their baseline scenario in our analysis to remain consistent with other studies, which do not account for changes in the reporting rate.
While estimates of \Ro and the associated confidence intervals for Study 6 in Table 1 represents estimates of \Ro based on $\bar G = 8\,\mathrm{days}$, we account for the uncertainty they consider for $\bar G$ in our formal analysis.

While most studies report confidence or credible intervals to quantify uncertainties associated with their estimates, some rely on different measures.
In particular, study 2 reports a range of \Ro for the worst and best case scenarios, which correspond to the values of \Ro such that 95\% and 5\% of the simulated total number of cases by January 18, 2020 is greater than or equal to 4000, respectively;
for brevity, we treat these intervals as a 90\% credible interval in our analysis.
Uncertainty ranges reported by Study 1 and Study 7 are assumed to be uniform ranges.

Some studies have now been published in peer-reviewed journals \citep{riou2020pattern, zhao2020preliminary} or have been updated with better uncertainty quantification \citep{readncov2}.
As our primary focus is on the resolution of uncertainty in the available information during the earliest stages of an epidemic, rather than to provide more precise or accurate estimate of \Ro, we strictly focus on estimates that were published between January 23--26, 2020.

@@

Here, we use the gamma approximation framework to the generation-interval distribution \citep{nishiura2009transmission, mcbryde2009early, roberts2011early, trichereau2012estimation, nishiura2015theoretical, park2019practical} to (i) characterize the amount of uncertainty present in the exponential growth rates and the shape of the generation-interval distribution and (ii) assess the degree to which these uncertainties affect the estimate of \Ro.
The gamma distribution provides a reasonable approximation for generation-interval distributions of many diseases, including Ebola, influenza, measles, and rabies.
Study 1, 5, 6, and 7 also used a gamma distribution (including delta and exponential distributions) to model the generation-interval distribution for SARS-CoV-2.
Assuming that generation intervals follow a gamma distribution with mean generation interval $\bar G$ and generation-interval dispersion $\kappa$, represented by the squared coefficient of variation of a gamma distribution, we have
\begin{linenomath*}
\begin{equation}
\Ro = \left(1 + \kappa r \bar{G}\right)^{1/\kappa}.
\label{eq:gamma}
\end{equation}
\end{linenomath*}
This equation demonstrates that a generation-interval distribution that has a larger mean (higher $\bar{G}$) or is less variable (lower $\kappa$) will give a higher estimate of \Ro for the same value of $r$ \citep{wallinga2007generation}.

@@

As most studies do not report their estimates of the exponential growth rate, we first re-estimate the exponential growth rate that correspond to their model assumptions.
Since the estimates of the basic reproductive number \Ro entirely depends on the exponential growth rate and the shape of generation-interval distributions, we can calculate the exponential growth rate from the basic reproductive number \Ro, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$.
First, to account for uncertainties in these parameters, we model reported values of the basic reproductive number \Ro, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$ with appropriate probability distributions.
We used gamma distributions to model values reported with confidence or credible intervals and uniform distributions to model values reported with ranges;
when confidence or credible intervals are reported, we parameterize the gamma distribution such that (i) its mean matches the estimated value and (ii) the probability that a random variable following the specified gamma distribution falls between the lower and upper confidence or credible limits is equal to the reported confidence or credible level. 
This probability does not need to be equi-tailed.
For example, Study 3 estimated $\Ro = 2.92$ (95\% CI: 2.28--3.67);
we model this estimate as a gamma distribution with a mean of 2.92 and a shape parameter of 67, which has a 95\% probability of containing a value between 2.28 and 3.67 (see Table 2 for a complete description).

For each study $i$, we construct a family of parameter sets by drawing $10^5$ random samples from the corresponding probability distributions (Table 2) that represent the estimates of $(\Ro)_{i,m}$ and the assumed values of $\bar G_{i,m}$ and $\kappa_{i,m}$ and calculate the exponential growth rate $r_{i,m}$ via the inverse of \eref{gamma}:
\begin{linenomath*}
\begin{equation}
r_{i,m} = \frac{\left[(\Ro)_{i,m}\right]^{\kappa_{i,m}} - 1}{\kappa_{i,m} \bar{G}_{i,m}},
\end{equation}
\end{linenomath*}
where $m=1,\dots,10^5$.
This allows us to approximate the probability distributions of the estimated exponential growth rates by each study.
We note that uncertainties in the probability distributions that we calculate for the estimated exponential growth rates reflects model assumptions, statistical methods, as well as quality of the data that each study relies on.
This assumption does not affect our analysis because we are re-estimating the probability distribution of $r_i$ that is consistent with the reported values of $(\Ro)_i$, $\bar G_i$, and $\kappa_i$;
in other words, we still obtain the same estimates and the associated uncertainty of $(\Ro)_i$ if we calculate it from $r_i$, $\bar G_i$, and $\kappa_i$.
For study 6, we fix $\bar G=8\,\textrm{days}$ and use the gamma distribution (Table 2) that corresponds to $\mathcal R_0 = 5.47$ (95\% CI: 4.16--7.10) during the re-estimation step for $r$ to remain consistent with the original study that assumed $\bar G=8\,\textrm{days}$ to obtain this particular estimate.
We account for uncertainties in $\bar G$ for Study 6 (Table 1) in all other steps in order to properly incorporate parameter uncertainties in the estimate of \Ro.
Study 7 uses the IDEA model \citep{fisman2013idea}, through which the authors effectively fit an exponential curve to the cumulative number of confirmed cases without propagating any statistical uncertainty.
Instead of modeling \Ro with a probability distribution and recalculating $r$, we use $r=0.114\,\mathrm{days}^{-1}$, which explains all uncertainty in the reported \Ro, when combined with the considered range of $\bar G$ in the original article.

>>>>

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

@@

\section*{Abstract}
A novel coronavirus (SARS-CoV-2) emerged as a global threat in December 2019. 
As the epidemic progresses, disease modelers continue to focus on estimating the basic reproductive number \Ro\ --- the average number of secondary cases caused by a primary case in an otherwise susceptible population.
The modeling approaches and resulting estimates of \Ro during the beginning of the outbreak vary widely, despite relying on similar data sources.
Here, we present a novel statistical framework for comparing and combining different estimates of \Ro across a wide range of models by decomposing the basic reproductive number into three key quantities: the exponential growth rate, the mean generation interval, and the generation-interval dispersion.
We apply our framework to early estimates of \Ro for the SARS-CoV-2 outbreak, showing that many \Ro estimates are overly confident.
Our results emphasize the importance of propagating uncertainties in all components of \Ro, including the shape of the generation-interval distribution, in efforts to estimate \Ro at the outset of an epidemic.

@@

As SARS-CoV-2 began to spread in parts of China outside Hubei province, as well as in other countries, many analyses of the outbreak were published as pre-prints (e.g., \cite{bedfordncov, imaincov, liuncov, majumderncov, readncov, zhaoncov}) and in peer-reviewed journals (e.g., \cite{li2020early, riou2020pattern, wu2020nowcasting, zhao2020preliminary}).
These analyses focused on estimating the basic reproductive number \Ro\ --- the average number of secondary cases generated by a primary case in a fully susceptible population \citep{anderson1991infectious, diekmann1990definition} --- in order to assess the pandemic potential of SARS-CoV-2.
Rapid dissemination of these early analyses played an important role in shaping the response to the outbreak \citep{majumder2020early}.

We commend these researchers for their timely contribution and those who made the data publicly available.
However, the estimates of \Ro from different research groups (as well as the associated degrees of uncertainty) vary considerably even though most analyses relied on similar data --- reports of confirmed cases from China, particularly from the Hubei province.
Comparing a disparate set of estimates of \Ro can be difficult when the estimation methods and their underlying assumptions vary widely.
In some cases, similar methods can give different estimates; in other cases, different methods can give similar estimates.
Understanding the differences between \Ro estimates is critical to controlling an epidemic as \Ro provides information about the level of intervention required to prevent further transmission \citep{anderson1991infectious}, and about the potential final size of the outbreak \citep{anderson1991infectious, ma2006generality}.

Here, we show that a wide range of approaches to estimating \Ro can be understood and compared in terms of estimates of three quantities: the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$.
The generation interval, defined as the interval between the time when an individual becomes infected and the time when that individual infects another individual \citep{svensson2007note}, characterizes the relationship between $r$ and \Ro \citep{wearing2005appropriate, roberts2007model, wallinga2007generation, park2019practical};
therefore, estimates of \Ro depend directly on their assumptions about the generation-interval distribution and the exponential growth rate.
Early in an epidemic, information is scarce and there is inevitably a great deal of uncertainty surrounding both case reports (affecting the estimates of the exponential growth rate) and contact tracing (affecting the estimates of the generation-interval distribution).
Ignoring these uncertainties leads to overly confident conclusions.
We suggest that disease modelers should make sure their assumptions about these three quantities are clear and reasonable, and that estimates of uncertainty in \Ro should propagate error from all three sources \citep{elderd2006uncertainty}.

We present a statistical framework for averaging across estimates of basic reproductive number \Ro from multiple studies and apply the method to seven disparate models published online as pre-prints between January 23--26, 2020 that estimated \Ro for the SARS-CoV-2 outbreak \citep{bedfordncov, imaincov, liuncov, majumderncov, readncov, riouncov, zhaoncov}.
Previous studies have directly calculated the average of reported \Ro values  \citep{majumder2020early, liu2020reproductive} but such methods mask differences in underlying model assumptions and statistical methods.
Instead, we decompose estimated \Ro into three key quantities ($r$, $\bar G$, and $\kappa$) and calculate the average (pooled estimates) of these key parameters.
Calculating \Ro based on the pooled estimates allows us to average appropriately across the uncertainties present in modeling approaches and in their underlying assumptions.
We use these pooled estimates to illustrate the importance of propagating different sources of error, particularly uncertainty in both the growth rate and the generation interval.

@@

\afterpage{%
\clearpage
    \begin{landscape}
\begin{table}[!th]
\begin{center}
\scriptsize
\begin{tabular}{l|L{2cm}|L{3.2cm}|L{2.8cm}|L{2.5cm}|L{2.4cm}|L{2.7cm}|L{2cm}}
 & Model & Data (study period) & Data source & Basic reproductive\newline number \Ro & Mean generation\newline interval $\bar G$ (days) & Generation-interval\newline dispersion $\kappa$ & Reference \\
\hline
Study 1 & Deterministic branching process model & Total number of cases in Wuhan City, China\newline (Jan 18, 2020) & Estimated by \cite{imaincov0} & 1.5--3.5 & 10 & 1 & \cite{bedfordncov} \\
\hline
Study 2 & Stochastic branching process model & Total number of cases in Wuhan City, China\newline (Jan 18, 2020) & Estimated by \cite{imaincov0}  & 2.6 (1.5--3.5)$^\ast$ & 8.4 & Not reported$^\dagger$ & \cite{imaincov} \\
\hline
Study 3 & Poisson offspring distribution model & Confirmed cases from China and other countries\newline (Dec 29, 2019--Jan 23, 2020) & Medical records and epidemiological investigations from Guangdong Province, China, and official websites of other regions in China & 2.92 (95\% CI: 2.28--3.67) & 8.4 & 0.2 & \cite{liuncov} \\
\hline
Study 4 & Metapopulation Susceptible-Exposed-Infected-Recovered (SEIR) model & Confirmed cases from China and other countries\newline (Jan 1--21, 2020) & Not reported & 3.8 (95\% CI: 3.6--4.0) & 7.6 & 0.5 & \cite{readncov} \\
\hline
Study 5 & Stochastic branching process model & Total number of cases in Wuhan City, China\newline (Jan 18, 2020) & Estimated by \cite{imaincov0} & 2.2 (90\% CI: 1.4--3.8) & 7--14 & 0.5 & \cite{riouncov} \\
\hline
Study 6 & Exponential growth model & Confirmed cases from China\newline (Jan 10--22, 2020) & Wuhan
Municipal Health Commission, China and National Health Commission of China & 5.47 (95\% CI: 4.16--7.10)$^\ddagger$ & 7.6--8.4 & 0.2 & \cite{zhaoncov} \\
\hline
Study 7 & Incidence Decay and Exponential Adjustment (IDEA) model & Reported cases from Wuhan City, China\newline (Dec 1, 2019--Jan 26, 2020) & World	Health Organization, National Health Commission of China, Wuhan Municipal	Health Commission, and \cite{huang2020clinical} & 2.0--3.1 & 6--10 & 0 & \cite{majumderncov} \\
\hline
\end{tabular}
\end{center}
\caption{
\textbf{Summary of the models, analyzed data, reported estimates of the basic reproductive number, and the assumptions about the generation-interval distributions.}
Model details, estimates of \Ro, and their assumptions about the shape of the generation interval distributions were collected from 7 studies.
Generation-interval dispersiosn represent the squared coefficients of variation in generation intervals.
$^\ast$These intervals reflect \Ro values for best and worst scenarios. We treat these intervals as a 90\% credible interval in our analysis.
$^\dagger$We assume $\kappa = 0.5$ in our analysis.
$^\ddagger$The authors presented \Ro estimates under different assumptions regarding the reporting rate; we use their baseline scenario in our analysis to remain consistent with other studies, which do not account for changes in the reporting rate.
}
\end{table}
\end{landscape}
\clearpage
}

We gathered information on estimates of \Ro and their model assumptions from seven articles that were published online between January 23--26, 2020.
Five studies \citep{liuncov, majumderncov, readncov, riouncov, zhaoncov} were uploaded to pre-print servers (bioRxiv, medRxiv, and SSRN); one report was posted on the website of Imperial College London \citep{imaincov}; and one report was posted on \url{nextstrain.org} \citep{bedfordncov} (Table 1).

@@

Despite a wide range of models considered across Study 1--7, all of them assume that the epidemic initially grows exponentially.
The IDEA model (used in Study 7) includes a discount parameter $d$ that allows the model to deviate from exponential growth when $d \neq 0$ \citep{fisman2013idea}, but Study 7 estimates $d=0$ across all parameters they consider.
Even though some studies consider reported cases up to January 26, 2020 --- three days after the travel restriction that took place on January 23, 2020 \citep{Tianeabb6105} --- the exponential growth assumption can still describe the number of reported cases reasonably well;
given the incubation period of around 5 days \citep{lauer2020incubation} as well as reporting delays of around 5 days \citep{sun2020early}, the majority of reported cases during the study periods are likely to have been infected prior to the travel ban.

When the epidemic is growing exponentially, the estimated basic reproductive number depends entirely on the exponential growth rate $r$ and the intrinsic generation-interval distribution $g(\tau)$, which describes the infection time of secondary cases caused by a primary case in a fully susceptible population \citep{champredon2015intrinsic}, via the Euler-Lotka equation \citep{wallinga2007generation}:
\begin{linenomath*}
\begin{equation}
\frac{1}{\Ro} = \int \exp(-r\tau) g(\tau) \, d\tau.
\label{eq:euler}
\end{equation}
\end{linenomath*}
In other words, all model assumptions reduce to assumptions about the exponential growth rate $r$ and the shape of the generation-interval distribution $g(\tau)$.
If a model relies on strong assumptions about the underlying observation or process model, the estimated confidence or credible intervals associated with the exponential growth rates or parameters of the generation-interval distributions will necessarily be narrow.
Therefore, it is sufficient to consider the estimates and assumptions about the exponential growth rates and the shapes of the generation-interval distributions to understand disparate estimates of the basic reproductive number.

As most studies do not report their estimates of the exponential growth rate, we first summarize model outcomes using reported (either estimated or assumed) values of the basic reproductive number \Ro, mean generation interval $\bar G$ and generation-interval dispersion $\kappa$, represented by the squared coefficient of variation (Table 1) ---
we re-estimate the corresponding exponential growth rates from these values later.
Study 2 only reports their assumptions about the mean generation interval; for simplicity, we assume $\kappa = 0.5$ in our analysis.
Study 6 presents \Ro estimates under 12 different scenarios regarding reporting rates (0, 0.5, 1 or 2 fold increase in reporting rate) and the shapes of the generation-interval distributions (MERS-like, SARS-like, and average);
we use their baseline scenario in our analysis to remain consistent with other studies, which do not account for changes in the reporting rate.
While estimates of \Ro and the associated confidence intervals for Study 6 in Table 1 are based on $\bar G = 8\,\mathrm{days}$, we account for the uncertainty they consider for $\bar G$ in our formal analysis.

While most studies report confidence or credible intervals to quantify uncertainties associated with their estimates, some use different measures.
In particular, Study 2 reports a range of \Ro for the worst and best case scenarios, which correspond to the values of \Ro such that 95\% and 5\% of the simulated total number of cases by January 18, 2020 are greater than or equal to 4000, respectively;
for simplicity, we treat these intervals as a 90\% credible interval in our analysis.
Uncertainty ranges reported by Study 1 and Study 7 are assumed to be uniform ranges.

Some of these studies have now been published in peer-reviewed journals \citep{riou2020pattern, zhao2020preliminary} or have been updated with better uncertainty quantification \citep{readncov2}.
As our primary focus is on the resolution of uncertainty in the available information during the earliest stages of an epidemic, rather than to provide more precise or accurate estimates of \Ro, we focus strictly on estimates that were published between January 23--26, 2020.

@@

Here, we use the gamma approximation framework to the generation-interval distribution \citep{nishiura2009transmission, mcbryde2009early, roberts2011early, trichereau2012estimation, nishiura2015theoretical, park2019practical} to (i) characterize the amount of uncertainty present in the exponential growth rates and the shape of the generation-interval distribution and (ii) assess the degree to which these uncertainties affect the estimate of \Ro.
The gamma distribution provides a reasonable approximation for generation-interval distributions of many diseases, including Ebola, measles, and rabies \citep{park2019practical}.
Studies 1, 5, 6, and 7 also used a gamma distribution (including the special cases of Dirac delta and exponential distributions) to model the generation-interval distribution for SARS-CoV-2.
Assuming that generation intervals follow a gamma distribution with mean generation interval $\bar G$ and generation-interval dispersion $\kappa$, represented by the squared coefficient of variation of a gamma distribution, we have \citep{park2019practical}:
\begin{linenomath*}
\begin{equation}
\Ro = \left(1 + \kappa r \bar{G}\right)^{1/\kappa}.
\label{eq:gamma}
\end{equation}
\end{linenomath*}
This equation demonstrates that a generation-interval distribution that has a larger mean (higher $\bar{G}$) or is less variable (lower $\kappa$) will give a higher estimate of \Ro for the same value of $r$ \citep{wallinga2007generation}.

@@

As most studies do not report their estimates of the exponential growth rate, we first re-estimate the exponential growth rate that corresponds to their model assumptions.
Since the estimates of the basic reproductive number \Ro depend entirely on the exponential growth rate and the shape of generation-interval distributions, we can calculate the exponential growth rate from the basic reproductive number \Ro, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$.
First, to account for uncertainties in these parameters, we model reported values of the basic reproductive number \Ro, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$ with appropriate probability distributions.
We used gamma distributions to model values reported with confidence or credible intervals and uniform distributions to model values reported with ranges;
when confidence or credible intervals are reported, we parameterize the gamma distribution such that (i) its mean matches the estimated value and (ii) the probability that a random variable following the specified gamma distribution falls between the lower and upper confidence or credible limits is equal to the reported confidence or credible level. 
This probability does not need to be equi-tailed.
For example, Study 3 estimated $\Ro = 2.92$ (95\% CI: 2.28--3.67);
we model this estimate as a gamma distribution with a mean of 2.92 and a shape parameter of 67, which has a 95\% probability of containing a value between 2.28 and 3.67 (see Table 2 for a complete description).

For each study $i$, we construct a family of parameter sets by drawing $10^5$ random samples from the corresponding probability distributions (Table 2) that represent the estimates of $(\Ro)_{i,m}$ and the assumed values of $\bar G_{i,m}$ and $\kappa_{i,m}$ and calculate the exponential growth rate $r_{i,m}$ by inverting \eref{gamma}:
\begin{linenomath*}
\begin{equation}
r_{i,m} = \frac{\left[(\Ro)_{i,m}\right]^{\kappa_{i,m}} - 1}{\kappa_{i,m} \bar{G}_{i,m}},
\end{equation}
\end{linenomath*}
where $m=1,\dots,10^5$.
This allows us to approximate the probability distributions of the exponential growth rates estimated by each study.
Uncertainties in the probability distributions that we calculate for the estimated exponential growth rates reflect model assumptions, statistical methods, as well as quality of the data that each study relies on.
This approach of re-estimating the exponential growth rate does not affect our analysis because we are re-estimating the probability distribution of $r_i$ that is consistent with the reported values of $(\Ro)_i$, $\bar G_i$, and $\kappa_i$;
in other words, we still obtain the same estimate and the same associated uncertainty of $(\Ro)_i$ if we calculate it from $r_i$, $\bar G_i$, and $\kappa_i$.
For study 6, we fix $\bar G=8\,\textrm{days}$ and use the gamma distribution (Table 2) that corresponds to $\mathcal R_0 = 5.47$ (95\% CI: 4.16--7.10) during the re-estimation step for $r$ to remain consistent with the original study, which assumed $\bar G=8\,\textrm{days}$ for this particular estimate.
We account for uncertainties in $\bar G$ for Study 6 (Table 1) in all other steps in order to properly incorporate parameter uncertainties in the estimate of \Ro.
Study 7 uses the IDEA model \citep{fisman2013idea}, through which the authors effectively fit an exponential curve to the cumulative number of confirmed cases without propagating any statistical uncertainty.
Instead of modeling \Ro with a probability distribution and recalculating $r$, we use $r=0.114\,\mathrm{days}^{-1}$, which accounts all uncertainty in the reported \Ro when combined with the considered range of $\bar G$ in the original article.

\newcommand{\gammdist}{\mathrm{Gamma}}
\begin{table}[t]
\begin{center}
\scriptsize
\begin{tabular}{l|p{5cm}|p{2.5cm}|p{2.7cm}}
 & Basic reproductive\newline number \Ro & Mean generation\newline interval $\bar G$ (days) & Generation-interval\newline dispersion $\kappa$ \\
\hline
Study 1 & $\mathrm{Uniform}(1.5, 3.5)$ & 10 & 1 \\
\hline
Study 2 & $\gammdist(\mathrm{mean}=2.6, \mathrm{shape}=18)$ & 8.4 & 0.5 \\
\hline
Study 3 & $\gammdist(\mathrm{mean}=2.92, \mathrm{shape}=67)$ & 8.4 & 0.2 \\
\hline
Study 4 & $\gammdist(\mathrm{mean}=3.8, \mathrm{shape}=1400)$ & 7.6 & 0.5 \\
\hline
Study 5 & $\gammdist(\mathrm{mean}=2.2, \mathrm{shape}=12)$ & $\mathrm{Uniform}(7, 14)$ & 0.5\\
\hline
Study 6 & $\gammdist(\mathrm{mean}=5.47, \mathrm{shape}=54)$ & $\mathrm{Uniform}(7.6, 8.4)^\ast$ & 0.2\\
\hline
Study 7 & $\exp(r \bar G)^\dagger$ & $\mathrm{Uniform}(6, 10)$ & 0\\
\hline
\end{tabular}
\end{center}
\caption{
\textbf{Probability distributions for \Ro, $\bar G$, and $\kappa$.}
We use these probability distributions to obtain a probability distribution for the exponential growth rate $r$.
The gamma distribution is parameterized by its mean and shape.
Constant values are fixed according to Table 1.
$^\ast$We do not account for this uncertainty during our re-estimation of the exponential growth rate $r$ because the reported estimate of $\mathcal R_0$ and its uncertainty assumes $\bar G = 8$.
We still account for this uncertainty in our pooled estimates ($\mu_G$).
$^\dagger$Instead of modeling \Ro with a probability distribution and re-estimating $r$, we use $r=0.114\,\mathrm{days}^{-1}$ (see text).
}
\end{table}
